Impacts of the exclusion of scientific surveys from closed areas on population indices, stock assessment, and conservation

### 2022-01-12 paper/paper.Rmd
notes on yellowmouth extrapolated index

The effect of restrictions on survey indicies depends on the variability and certainty in the status quo index, as well as the proportion of the species' population occurs inside the restricted areas (Figures \@ref(fig:indices) for highlights, and \@ref(fig:indices-hs), \@ref(fig:indices-qcs), \@ref(fig:indices-wchg), \@ref(fig:indices-hbll) for all species-survey combinations with converged models).
Extrapolation can either over or underestimate the index for a given survey in a given year (solid orange line vs. dotted grey line in Figure \@ref(fig:indices)). 
Shrinking the survey index to exclude restricted areas consistently lowers the total index to a degree proportional to the species' average abundance within the restricted areas, but otherwise parallels the extrapolated index (blue line vs. orange line in Figure \@ref(fig:indices)).
CV ratios greater than 1 represent reduced precision of index estimates relative to the status quo index; the shrunk index loses less precision (has lower CV ratios) than the extrapolated index (blue dots lower than orange ones in Figures \@ref(fig:hbll-plots)a-b and \@ref(fig:qcs-plots)a-b). 
However, this increase in precision has little

@@

```{r mare-by-cv-ratio, out.width="\\textwidth", fig.cap="..."}
include_graphics(here("figs/explore-all-mare-by-cv-ratio.pdf"))
```

@@

```{r indices-qcs, out.width="\\textwidth", fig.cap="SYN QCS indices calculated from a geostatistical model."}
include_graphics(here("figs/index-qcs-geo-restricted.pdf"))
```

>>>>

The effect of restrictions on survey indicies depends on the variability and certainty in the status quo index, as well as the proportion of the species' population occurs inside the restricted areas (Figures \@ref(fig:indices) for highlights, and \@ref(fig:indices-hs), \@ref(fig:indices-qcs), \@ref(fig:indices-wchg), \@ref(fig:indices-hbll) for all species-survey combinations with converged models).
Extrapolation can either over or underestimate the index for a given survey in a given year (solid orange line vs. dotted grey line in Figure \@ref(fig:indices)). 
Shrinking the survey index to exclude restricted areas consistently lowers the total index to a degree proportional to the species' average abundance within the restricted areas, but otherwise parallels the extrapolated index (blue line vs. orange line in Figure \@ref(fig:indices)).
CV ratios greater than 1 represent reduced precision of index estimates relative to the status quo index; the shrunk index loses less precision (has lower CV ratios) than the extrapolated index (blue dots lower than orange ones in Figures \@ref(fig:hbll-plots)a-b and \@ref(fig:qcs-plots)a-b). 
However, this increase in precision does not improve accuracy (reduce MARE; \@ref(fig:mare-by-cv-ratio)).

@@

```{r mare-by-cv-ratio, out.width="\\textwidth", fig.cap="MOVE TO SUPPLEMENT? Note the CV ratio for SYN QCS survey Yellowmouth Rockfish is actually > 2."}
include_graphics(here("figs/explore-all-mare-by-cv-ratio.pdf"))
```

@@

```{r indices-qcs, out.width="\\textwidth", fig.cap="SYN QCS indices calculated from a geostatistical model. Note that CI on Yellowmouth Rockfish extrapolated index is truncated."}
include_graphics(here("figs/index-qcs-geo-restricted.pdf"))
```
